---
title: "Class Project"
output: github_document
---
  
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
library(ggplot2)
library(dplyr)
load("data/consumer_complaints_data.Rdata")
data <- select_res 
map_data <- data[, c("Complaint ID", "Company", "State")]

counts <- map_data %>%
  group_by(State) %>%
  summarise(complaint_count = n()) %>% 
  arrange(desc(complaint_count))

counts$State <- factor(counts$State, levels = counts$State)

ggplot(counts, aes(x = State, y = complaint_count)) +
  geom_bar(stat = "identity") +
  labs(title = "Complaint Counts by State", x = "State", y = "complaint_count") +
  theme(axis.text.x = element_text(angle = 75, hjust = 1))
```

#Time Response Distribution#
```{r}
library(dplyr)
library(ggplot2)
product_distribution <- select_res %>%
  group_by(Product) %>%
  summarize(
    Count = n(),
    Percentage = Count / nrow(select_res) * 100
  ) %>%
  arrange(desc(Count))
product_distribution

timely_response <- (sum(select_res$`Timely response?` == "Yes"))/52550
print(timely_response)
ggplot(select_res, aes(x = `Timely response?`)) +
  geom_bar(fill = "black") +
  labs(
    title = "Timely Response Distribution",
    x = "Timely or No",
    y = "Count"
  ) +
  theme_minimal()
```
#Complaints by States Among Finance Companies#
```{r}
consumer_data <- select_res
library(tidyverse)

Fin_company <- c('Citybank', 'Bank of America', 'HSBC North America Holdings Inc.', 'Discover')
finance_data <- consumer_data %>% 
  filter(Company %in% Fin_company) %>% 
  group_by(State) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
finance_data
```

#Complaints of BOA in 2014#
```{r}
BOA <- consumer_data %>% 
  filter(Company == 'Bank of America',
         year(`Date received`) == 2014) %>% 
  mutate(Cmonth = month(`Date received`))

BOA <- BOA %>% 
  group_by(Cmonth) %>% 
  summarise(count = n())

library(ggplot2)

ggplot(BOA, aes(x = Cmonth, y = count))+
  geom_point()+
  geom_line()+
  theme_minimal()+
  labs(
    title = 'Complaints of BOA',
    x = 'Month',
    y = 'Number of complaints'
  )
```

